### 2016-12-28 MSSM/MSSM.tex
Adding more MSSM selection

\subsection{\texorpdfstring{Event selection in the \emu channel}{Event selection in the e mu channel}}
\label{sec:mssm_eventsel_em}
Events in the \emu channel are first selected by a trigger
that requires an electron and muon at \ac{L1} and applies loose ID and
isolation requirements to these objects at \ac{HLT}.

@@

\section{Discriminating variable}
\label{sec:mssm_discrvar}

\section{Background estimation}
\label{sec:mssm_bkgs}

@@

>>>>

\subsection{\texorpdfstring{Event selection in the \emu channel}{Event selection in the e mu channel}}
\label{sec:mssm_eventsel_em}
Events in the \emu channel are first selected by two triggers
that both require an electron and muon at \ac{L1} and apply loose ID and
isolation requirements to these objects at \ac{HLT}. The \pT requirements on
the electron and muon are different in the two triggers, thus using the combination of the two
improves the analysis performance.

The offline requirements to the \emu pair are that the electron 
and muon are oppositely charged, separated by $\Delta R >$ 0.3. The 
electron should have a minimum \pT~ of 13 GeV and have $|\eta|< 2.5$. As
in the \etau channel the electron's impact parameters have to 
satisfy $d_{xy} < 0.045$ cm and $d_{z}<0.2$ cm. A selection is
made on the electron identification MVA, using a working point that 
is 80\% efficient for electrons in \Zee decays. The electron
also needs to be isolated, with the relative isolation calculated
with a cone size of 0.3 being less than $<0.15$.

The muons need to have a \pT~of at least 10 GeV, $|\eta|<2.4$ and 
their impact parameters need to be $d_{xy}<0.045$ cm and $d_{z}<0.2$ cm.
In addition to the kinematic requirements the muon must
pass the medium identification criteria and be isolated with the relative
isolation, calculated with a cone size of 0.4, required to be less than 0.15.

Because a combination of triggers is used, the object firing
the higher \pT~ trigger leg needs to have a transverse momentum
of at least 24 GeV on top of the requirements already discussed.
In addition, a topological selection is made on the $D_{\zeta}$ variable \cite{cdf-dzeta},
\begin{align}\label{eqn:mssm_em_dzeta}
D_{\zeta} = P_{\zeta} - 1.85 P_{\zeta}^{\text{vis}}, \notag \\
\text{where } P_{\zeta} = (\vec{p}_{\text{T},1}^{\text{vis}} + \vec{p}_{\text{T},2}^{\text{vis}} + E_{\text{T}}^{\text{miss}})\frac{\vec{\zeta}}{|\vec{\zeta}|}, \notag \\
\text{and } P_{\zeta}^{\text{vis}} = (\vec{p}_{\text{T},1}^{\text{vis}}+\vec{p}_{\text{T},2}^{\text{vis}})\frac{\vec{\zeta}}{|\vec{\zeta}|}.
\end{align}

Thus $D_{\zeta}$ is the difference of the projection of the visible tau decay products plus missing energy \pT+\MET,
and simply the visible tau decay product \pT on the axis $\vec{\zeta}$. This is the axis that bisects 
the directions $\vec{p}_{\text{T,1}}^{\text{vis}}$ and $\vec{p}_{\text{T,2}}^{\text{vis}}$
of the visible decay products in the transverse plane. This selection is illustrated in figure
\ref{fig:mssm_dzeta}a, with figure \ref{fig:mssm_dzeta}b showing the $D_{\zeta}$ distribution
for \emu events. The used cut value, $D_{\zeta} > -20$ GeV rejects $\ttbar$, \Wjets and diboson
events.

\begin{figure}[h!]
\begin{center}
\subfloat[Reconstruction of $D_{\zeta}$]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
\subfloat[$D_{\zeta}$ distribution in \emu channel]{./includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
\end{center}
\caption{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
\emu channel\cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_dzeta}
\end{figure}

@@

\section{Discriminating variable}
\label{sec:mssm_discrvar}
The discriminating variable used for signal extraction is the total transverse mass,
\begin{equation}\label{eqn:mttot}
m_{\text{T}}^{\text{tot}} = \sqrt{(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_1^{\text{vis}}))^2+
(m_{\text{T}}(E_{\text{T}}^{\text{miss}},\tau_2^{\text{vis}}))^2 + (m_{\text{T}}(\Pgt_1^{\text{vis}},\Pgt_2^{\text{vis}}))^2}.
\end{equation}

$m_{\text{T}}(1,2)$ is defined as,
\begin{equation}\label{eqn:mttot_12}
m_{\text{T}}(1,2) = \sqrt{2p_{\text{T},1}p_{\text{T},2}(1-\cos{(\Delta\phi(1,2))})}.
\end{equation}

This means that $m_{\text{T}}(E_{\text{T}}^{\text{miss}},\Pgt_1^{\text{vis}})$ is equivalent
to the \mT~ defined for the \etau and \mutau channels in equation \ref{eqn:hhh_selection_mt}.
The \mTtot~ variable provides good separation between signal and QCD multi--jet events
in the \etau, \mutau and \tautau channels, and between
signal and \ttbar events in the \emu channel.

\section{Background estimation}
\label{sec:mssm_bkgs}
The methods used for background estimation will be described in this
channel. The background estimation in the \etau and \mutau channels
is very similar and they are combined

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-a.pdf}
\end{center}
\caption{Exclusion in the $m_{h}^{\text{mod}+}$ scenario obtained by the combination
of all channels in the \AHtotautau analysis. The blue shaded area bounded by the 
solid black line is the observed exclusion, with the dashed black line the
expected exclusion. The grey bands indicate the $\pm 1,2$ $\sigma$ 
expected exclusion. The red shaded area
is excluded by the lack of a light Higgs boson with mass compatible with 125 GeV \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_mhmodp_2016}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure_012-b.pdf}
\end{center}
\caption{Exclusion in the hMSSM scenario obtained by the combination
of all channels in the \AHtotautau analysis. The blue shaded area bounded by the 
solid black line is the observed exclusion, with the dashed black line the
expected exclusion. The grey bands indicate the $\pm 1,2$ $\sigma$ 
expected exclusion \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_hmssm_2016}
\end{figure}
